---
title: "Data-Products Diamond"
author: "Victoria Meo"
date: "November 17, 2016"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Information about the data set Diamonds



####Description
A dataset containing the prices and other attributes of almost 54,000 diamonds. The variables are as follows:

- price = price in US dollars (\$326--\$18,823)
- carat =  weight of the diamond (0.2--5.01)
- cut = quality of the cut (Fair, Good, Very Good, Premium, Ideal)
- colour =  diamond colour, from J (worst) to D (best)
- clarity = a measurement of how clear the diamond is (I1 (worst), SI1, SI2, VS1, VS2, VVS1, VVS2, IF (best))
- x = length in mm (0--10.74)
- y = width in mm (0--58.9)
- z = depth in mm (0--31.8)
- depth = total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43--79)
- table = width of top of diamond relative to widest point (43--95)



## Interactive Plot

```{r}
library(shiny)
library(ggplot2)

shinyApp(
        UI(pageWithSidebar(
        headerPanel('Diamond DataTable'),
        sidebarPanel(
                checkboxGroupInput('show_vars',
                                   'Columns in diamond table to be shown:',
                                   names(diamonds),
                                   selected = names(diamonds)),
                helpText('Note: You can choose what columns are shown in the table by checking the box.')
                ),
        mainPanel(
                tabsetPanel(
                        h3('diamonds',
                                 dataTableOutput("mytable1"))


                )
        )
                )),

        Server = function(input, output) {

        # a large table, showing variables of the diamonds
        output$mytable1 <- renderDataTable({
                datatable(diamonds[, input$show_vars, drop = FALSE]
        }),

         options = list(height = 500)
        
        )


```

## Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## R Output

```{r cars}
summary(cars)
```


