---
title: "Data Products - Diamonds"
author: "Victoria Meo"
date: "November 17, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Information about the data set Diamonds



####Description
A dataset containing the prices and other attributes of almost 54,000 diamonds. The variables are as follows:

- price = price in US dollars (\$326--\$18,823)
- carat =  weight of the diamond (0.2--5.01)
- cut = quality of the cut (Fair, Good, Very Good, Premium, Ideal)
- colour =  diamond colour, from J (worst) to D (best)
- clarity = a measurement of how clear the diamond is (I1 (worst), SI1, SI2, VS1, VS2, VVS1, VVS2, IF (best))
- x = length in mm (0--10.74)
- y = width in mm (0--58.9)
- z = depth in mm (0--31.8)
- depth = total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43--79)
- table = width of top of diamond relative to widest point (43--95)

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r, echo = TRUE}
library(ggplot2)
summary(diamonds)
```

## Slide with Plot

```{r}
library(ggplot2)
library(shiny)

table(diamonds)
```


