---
title: "Diamonds"
author: "Victoria Meo"
date: "November 20, 2016"
output: 
  ioslides_presentation: 
    smaller: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diamond Data Set: 
##### Dataset containing the prices and other attributes of almost 54,000 diamonds
##### Variables defined

- Price = the price in US Dollars 
- Carat = weight
- cut = quality (fair, good, Very Good Premium, Ideal)
- Colour = J worst, D best
- Clarity - how cear (I1 (worst), SI1, SI2, VS1, VS2, VVS1, VVS2, IF (best))
- x = length in mm (0--10.74)
- y = width in mm (0--58.9)
- z = depth in mm (0--31.8)
- depth = total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43--79)
- table =  width of top relative to widest point (43--95)

## Sample of the dataset

```{r, echo=TRUE}
library(ggplot2)
data("diamonds")
head(diamonds)
```
## Code for Interactive Table

```{r, echo = TRUE, eval=TRUE}
shinyApp(
        shinyUI(pageWithSidebar(
        headerPanel('Diamond Data Table'),
        sidebarPanel(
                checkboxGroupInput('show_vars',
                                   'Colums in diamond table to be shown',
                                   names(diamonds),
                                   selected = names(diamonds)),
                helpText('Note: You can choose what columns are shown in the table by checking the box.')
        ),
        mainPanel(
                h3(textOutput("Diamonds")),
                dataTableOutput("mytable1")
        )
)),
shinyServer(function(input, output) {

        # a large table, showing variables of the diamonds
        output$mytable1 = renderDataTable({
                library(ggplot2)
                diamonds[, input$show_vars, drop = FALSE]
        })


})
)
```



## Thank you 

This presentation includes the definitions of the variables associated with the data set
It also includes a sample of the data
Finally is the code i used to create the slidy datable

This link below will take you to the actual datatable

https://victoriameo.shinyapps.io/DiamondDataProducts/

Hope you enjoy
